
% Abstracts are usually written in English, with a version in your
% mother tongue underneath
\chapter*{Abstract} 
\addcontentsline{toc}{chapter}{Abstract}
% Don't change anything above this.
\Jnote{Mention that Zika epidemy is very recent and there is not much
  work done yet.}
Since its emergence Zika virus has been modelled with traditional compartmental models ,
\Jnote{Space after comma.}
where the population is assumed to be well mixed.
This assumption is unrealistic hence  we build a Zika virus model on a small world network, to describe the behaviour and course of Zika virus.
\Jnote{Last sentence is too strong. You don't know how realistic it is.
  Write sth like ``we study a different approach based on small world networks
  and compare it with the uniform model''}

Small world networks, introduced by Strogatz and Watts, on the other hand assume that you are more likely to spread the disease to someone in your family, someone who lives near you, or someone you know.
\Jnote{Do not address reader directly (``you''). Use passive voice.}
It combines
\Jnote{``It combines'' What  is ``it''?}
this sort of clustering in the graph with a probability to model the spread of disease as a dynamical system.

% At a unviersity like Stellenbosch you *must* produce an abstract in Afrikaans for your masters.
% At AIMS you are encouraged to repeat the abstract in your mother tongue
% French, Igbo, Mlagasy, etc. just write it using LaTeX's special
% characters.
% Arabic students see the arabic.tex file for an example
% Amharic use openoffice and export from there and import a figure here.
% Where the words do not exist put the English work in italics, or use mathematical symbols.




