

\chapter{Connection between parallel repetition of multi-prover games and  Hales-Jewett theorem.}

This chapter presents the relationship between parallel repetition of multiple provers with the density Hales-Jewett theorem. We give a parallel repetition bound using the density Hales-Jewett. Firstly, we show that the density Hales-Jewett theorem implies parallel repetition. Secondly, we show that the parallel repetition implies the density Hales-Jewett theorem.

\section{Hales-Jewett theorem implies parallel repetition.}

In both versions of Hales-Jewett theorem (see \eqref{hj1} and \eqref{hj2}), the concept which emphasizes this theorem is the \textit{combinatorial line.} The combinatorial line is the umbilical cord between the Hales-Jewett theorem and the parallel repetition. In section \eqref{hjt}, we have already explain deeply
\Jnote{s/deeply/in a detailed way}
and define what the combinatorial is. Let us recall some notions about a combinatorial line and the formulation of the Hales-Jewett theorem.

Let $k, n\in \mathbb{Z}^+$, $[k]=\{1,2, \ldots,k\}$ and an $x-$string $w(x)=a_1a_2\ldots a_n \in ([k]\times\{x\})^n\setminus [k]^n.$ That is, in $w(x)=a_1a_2\ldots a_n$, at least one of the symbol   $a_i$ contains the symbol  $x$ called wildcard. Let $w(x;i)$ be the string obtained by replacing $x$ by $i$.

The \textit{combinatorial line} is the set of $k$ strings $\{w(x;i): \ i\in \{1,2,\ldots,k\} \}$, that is the set $\{w(x;1), w(x;2), \ldots, w(x;k)\}.$ 
 
So, in \eqref{hj1}  the Hales-Jewett theorem is given.
\Jnote{Don't start sentence with ``So''. You can say ``HJ theorem is given in ()''.}
As the name stipulates, the Hales-Jewett was proved by Hales and Jewett. The formulation is based on colouring of a set and on the existence of s a monochromatic combinatorial line.

Furthermore, there is a density formulation of Hales-Jewett theorem on which this section is mainly constructed. Given a subset $A$ of $[k]^n$, the density of $A$ is defined and denoted as $\delta(A)=\frac{|A|}{k^n}.$ By simplicity, $\delta$ denotes the density of $A$, that is $\delta=\delta(A).$

Thereby, the density version of Hales-Jewett theorem states that for any positive number $k$ and real number $\delta$,  there exists a large enough number $n$ (depending on $k$ and $\delta$) such that  any subset of  $[k]^n $ with density $\delta$ contains a combinatorial line.
%\Jnote{It is not necessary to repeat concepts from the previous chapter in   such detailed way.}
In the following, essentially  we use  the density version of  Hales-Jewett theorem. Whenever there is Hales-Jewett theorem, it means the density version of Hales-Jewett theorem.
\Jnote{s/Whenever there is/Whenever we say} 

We denote by $\Delta_{k,n}$ the maximum density of a subset $W$ of $[k]^n$ without a combinatorial line. We have discussed a lot on this in \eqref{dhjn}.
\Jnote{Ref is broken. s/We have discussed a lot/Delta\_kn was discussed in}
The number $\Delta_{k,n}$ is called density Hales-Jewett number.

The theorem thereafter has been formulated and demonstrated  by Hillel Furstenberg and Yitzhak Katznelson  during their work on a density version of Hales-Jewett theorem.
\Jnote{It is still misleading. It was not demonstrated ``during their work on DHJ''.
  It \emph{is} the DHJ! I mean it is easy to see that it is equivalent to Theorem 2.4.2.
Please say this.}

\begin{thm}[\cite{furstenberg1991density}]	For $k\geq 2$, $\lim\limits_{n\longrightarrow \infty} \Delta_{k,n}=0.$ \label{fk}	\end{thm}
%\Jnote{Be clear that this \emph{is} the density Hales-Jewett theorem!   Hales-Jewett was proved by Hales and Jewett and the density version   (density Hales-Jewett) was proved by Furstenberg and Katznelson.}
 
This theorem states that for $k\geq 2$, the maximum  density of a subset of $[k]^n$ without a combinatorial line converges to $0$ when $n$ converges to infinity. That is,
the set $[k]^n$
\Jnote{s/the set/a subset of $[k]^n$ with constant measure}
will almost necessary
\Jnote{almost necessary/necessarily}
contains a subset with a combinatorial line when $n$ increases.

The proof of this theorem has been given by \cite{furstenberg1991density} without explicit bounds. \cite{polymath2012new} gave an upper bound of $\Delta_{k,n}$ for a particular case ($k=3$): $\Delta_{3,n} \leq O(1/\sqrt{\log^* n}).$ Previously, a lower  density Hales-Jewett bound  was known through the work of \cite{polymath2010density} who establishes that  for $k\geq 3$, $\Delta_{k,n} \geq \exp \left(-O(\log n)^{1/l}\right)$ where $\ell$ is the largest integer such that $2k > 2^{\ell}$. This lower bound can simply be written as: $\Delta_{k,n} \geq \exp \left(-O(\log n)^{1/\lceil \log_2 k \rceil}\right)$ where $\lceil x \rceil$=ceilling$(x)$ is the least integer greater than or equal to $x.$ For $k=2$, the density Hales-Jewett number is: $\Delta_{2,n}=\Theta(1/\sqrt{n})$ known by Sperner's theorem.
\Jnote{This paragraph belongs to previous chapter.}
`

Hillel Furstenberg and Yitzhak Katznelson's theorem \eqref{fk} and the Raz theorem \eqref{prt} are close but not equivalent. Let us recall what Raz theorem is. 
The Raz theorem \eqref{prt} has been conjectured by \cite{feige1992two} and demonstrated by \cite{raz1998parallel}. This conjecture states that the value of a parallel repetition of a game (non trivial) decreases exponentially  fast to $0$ when $n$ converges to infinity.  It is clear that the convergence of Raz theorem is fast than the convergence of Hillel Furstenberg and Yitzhak Katznelson's theorem. Thus, the Raz theorem appears to be bounded by the density of the largest subset without a combinatorial line.
\Jnote{No, it is not. The theorems are uncomparable. If you take very large
  answer alphabet size Raz becomes useless while Verbitsky still works.
  If you take constant alphabet size and epsilon Raz theorem is much faster.}
The following Oleg Verbitsky theorem  shows that the density Hales-Jewett theorem implies the parallel repetition of multi-prover games.

\begin{thm}[\cite{verbitsky1996towards}]	 Let $G$ be a non-trivial multi-prover game with $|Q|=r$ the size of question set. Then, 
  $$\val (G^n) \leq \Delta_{r,n}.$$	\label{ver96} \end{thm}

Applying the theorem of Hillel Furstenberg and Yitzhak Katznelson in \eqref{fk}, we obtain the following consequence.
\begin{cor}	Let $G$ be a non-trivial multi-prover game. Then, $\lim\limits_{n\longrightarrow \infty} \val (G^n)=0.$ 	\end{cor}

The theorem \eqref{ver96}  has been proved by \cite{verbitsky1996towards} for two-prover games.  His proof can be extended for  multi-prover games in our case,  that is, for $k$ players with $k\geq 2.$ To establish the truth of  this theorem, Oleg Verbitsky used the proof by contradiction. The general idea is: given a subset $W$ of $Q^n$, we must show that $W$ is  the subset of $Q^n$ without a combinatorial line.
\Jnote{Say that $W$ is the subset of $Q^n$ for which the provers win
  for a given strategy.}

So, we assume that there is a combinatorial line and then we show that there is  contradiction.

Let us adapt our proof from the proof of  \cite{verbitsky1996towards} to show the theorem \eqref{ver96} for multi-prover games, that is, we extend the proof of Oleg Verbitsky from two-prover games to multi-prover games.

\begin{proof}
  Let $G$ be a $k-$prover game, that is $G(\phi, Q\subseteq X^1 \times \ldots \times X^k, A^1 \times \ldots \times A^k, \mu)$ where $X^t$ and $A^t$ represent respectively the set of questions and the set of answers of the player $t$, for $1\leq t \leq k.$ The set $Q$ is a subset of the set $X^1 \times \ldots \times X^k$ where elements are chosen randomly  according to the probability distribution $\mu$.
  \Jnote{For this proof you have to assume that $\mu$ is uniform.}

 Let $|Q|=r$, with $Q=\{q_1, \ldots, q_r\}$ where $q_j=(q_j^1,\ldots, q_j^k)$, $q_j^t \in X^t$ for $j\leq r.$ The superscript  $t$ highlights the component (player), while the subscript $j$ denotes the number (order) of questions. For instance the question $q_j^t$ is the $j-$th question addressed to the player number $t.$  For the parallel repetition $G^n$, let us consider $F^1, \ldots, F^k$ like the $k$ optimal strategies of the game where each strategy is an $n-$tuple function of strategies, that is $F^t=(f_1^t,\ldots, f_n^t)$. We denote by $K$ the set of success questions using these strategies in $G^n.$ The set $K$ can be expressed as: 
 
 $K=\{(s_1, \ldots, s_n) \in Q^n: \bigwedge\limits_{i=1}^n \phi \left[ s_i^1, \ldots, s_i^k, f_i^1(s_1^1, \ldots, s_n^1), \ldots, f_i^k(s_1^k, \ldots, s_n^k) \right]=1 \}.$
 \Jnote{Before the proof you used $W$, now you use $K$. Be consistent.}

Note that for $1\leq i \leq n$,  $s_i \in Q=\{q_1, \ldots, q_r\}.$ $s_i^t$ denotes an $i-$th question in parallel repetition addressed to the player $t$. This question can be any of the $t-$th component of the set  $q_j.$
 
As $K$ is the set of success questions, then the value of the game $G^n$ is: $\val (G^n) = \frac{|K|}{r^n}.$
\Jnote{Note that this is the place where you use uniform distribution assumption}.
 
In this stage, we can not say that $\Delta_{r,n} \geq \frac{|K|}{r^n}$
%\Jnote{Not equal, it should be $\ge$.}
because we do not know if the set  $K$ does not contain any combinatorial lines. Let us show that $K$ is a set without a combinatorial line.

Let us suppose by contradiction that there is a combinatorial line $L=\{\bar{b}_1, \ldots, \bar{b}_r \} \subseteq K.$ In this case,  the game  $G$ should be trivial.
%\Jnote{Game $G$ has nothing to do with the proposition.}
 
Let $C=C_1\ldots C_n$ be an $r \times n$ matrix whose $r$ rows are $\bar{b}_1, \ldots, \bar{b}_r$ and $n$ columns $C_1\ldots C_n$ each are either $(q_j,q_j,\ldots,q_j)^T$ for some $j\leq r$ or $(q_1,q_2,\ldots,q_r)^T.$ By definition of a combinatorial line, there exists at least one column $C_l=(q_1,q_2,\ldots,q_r)^T.$ We assume that $L$ is ordered so that the intersection of the row $\bar{b}_j$ and the column $C_l$ of the matrix is the element $q_j.$ The element $q_j=(q_j^1,\ldots, q_j^k)$ has $k$ components. So, the  matrix $C$ can be expanded to the $kr \times n$ matrix $D$ by replacing each matrix element $q_j$ with the column $(q_j^1,\ldots, q_j^k)^T.$ There are $kr$ rows of the matrix D and $n$ columns. Thus, let us denote by $\bar{x}_1^1, \ldots, \bar{x}_1^k, \ldots, \bar{x}_r^1, \ldots, \bar{x}_r^k$ the rows of the matrix $D$ where $\bar{x}_j^t \in  (X^t)^n.$

Since $L$ is a combinatorial line, let us use one of the strategy of the matrix element in the column $C_l$ which is in the form $(q_1,q_2,\ldots,q_r)^T.$  Note that $q_j$ is a $k-$tuple. 
Let us define strategies $f^1,f^2, \ldots, f^k$ in the game $G$ by $f^t(q^t)=f_l^t(\bar{x}_{n_t}^t)$ where $x_{n_t}^t=q^t$ for $1\leq t \leq k.$ These strategies $f^t$ are well defined, since for distinct such $n_t$ and $n_t'$ it holds $\bar{x}_{n_t}^t= \bar{x}_{n_t'}^t.$
\Jnote{I don't understand last sentence.}

For  arbitrary $q_j= (q_j^1,\ldots, q_j^k) \in Q$, we have:
$$\phi (q^1,\ldots, q^k, f^1(q^1), \ldots, f^k(q^k))= \phi (q_j^1,\ldots, q_j^k, f_l^1(\bar{x}_j^1), \ldots, f_l^k(\bar{x}_j^k))=1$$

As $b_j \in K$, strategies $F^1, \ldots, F^k$ win in  the $l-$th copy of $G$. That is the game $G$ is not trivial. \Jnote{It \emph{is} trivial.}

Hence, there is a contradiction with our assumption that $K$ contains a combinatorial line.

Therefore, $K$ does not contain a combinatorial line and $\Delta_{r,n} \geq  \frac{|K|}{r^n}$.
%\Jnote{Change $=$ to $\le$.}
It results that $\val (G^n) \leq \Delta_{r,n}.$
\end{proof}

Let $\nu_{Q,n}=\max_G \val (G^n)$ where the maximum is over all non-trivial games $G$ with set of questions $Q.$ 
The Oleg Verbitsky's theorem \eqref{ver96} is applicable to $\nu_{Q,n}$, that is $\nu_{Q,n} \leq \Delta_{r,n}.$
\Jnote{What is $r$?}
Then, $\lim\limits_{n\longrightarrow \infty} \nu_{Q,n}=0.$

\section{Parallel repetition implies Hales-Jewett theorem.}
 
To show that the parallel repetition implies Hales-Jewett theorem, let us firstly define a set of questions on which will be constructed some multi-prover games.

\begin{defn}Let $k\geq 2$ and $Q_k \subseteq \{0,1\}^k$ a question set of size $k.$ An \textit{k-prover question set} is a question set $Q_k$ where the $t-$th question contains $1$ in the $t-$th position and $0$ in the remaining positions. This question set can be expressed as:
$$Q_k=\left\lbrace(q^1, \ldots, q^k): |\{t:q^t=1\}|=1\right\rbrace.$$		\end{defn}
 
 An extensional definition of the question set $Q_k$ is: $Q_k=\left\lbrace (1,\ldots,0), (0,1,\ldots,0), \ldots, (0,\ldots,1) \right\rbrace.$ $|Q_k|=k$ and the elements of the question set $Q_k$ are equivalent to the elements of the canonical basis, that is $Q_k= \left\lbrace e_1, e_2, \ldots, e_k\right\rbrace$ where $e_l=(\delta_{1l}, \delta_{2l}, \ldots, \delta_{kl} )$, $\delta_{ml}$ is the Kronecker delta which equals to $1$ if $l=m$ and $0$ whenever $l \neq m$ for $1 \leq l, m \leq  k.$ 
 
 
 Raz theorem can be applied for this question set $Q_k$.
 \Jnote{It cannot be applied because it is just for two provers.}
 Let $G$ be a multi-prover game with question set $Q_k$ and $\val (G^)$ the value of the $n-$product of $G.$  Then, the question set $Q_k$ admits parallel repetition if $ \val (G^n)$ converges to $0$ when $n$ converges to infinity.
 Also, according to Raz theorem,
 \Jnote{Delete ``according to Raz theorem''.}
 the question set $Q_k$  admits exponential parallel repetition if there exists $\xi_{Q_k} < 1$ such that for every $n \in \mathbb{N}$: $$\val (G^n) \leq (\xi_{Q_k})^n.$$
\Jnote{This paragraph is not relevant to this section.}

The following theorem highlights that there exists a game such that the parallel repetition of this game  implies the density Hales-Jewett theorem. This result announced as theorem \eqref{hka} links the existence of a combinatorial line in a set with the parallel repetition value of a certain game.

\Jnote{Use \textbackslash cite* to cite.}
 \begin{thm}[\cite{hkazla2016forbidden}] Let $k\geq 3$, $n\geq 1$ and $S\subseteq [k]^n$ with density $\delta=|S|/k^n$ such that $S$ does not contain a combinatorial line.	
 
There exists a $k-$prover game $G_S$ with question set $Q_k$ and with answer alphabets,
$A^t = 2^{[n]} \times [n]$ such that:
\begin{itemize}
\item $\val (G_S) \leq 1-1/k.$ 	\item $\val (G_S^n) \geq \delta(S).$
\end{itemize} \label{hka}
 	\end{thm}

Thus, from the theorem \eqref{hka} we can deduce the value of the $n-$fold parallel repetition $G_S^n$ when $S$ is the maximum subset of  $S\subseteq [k]^n$ without a combinatorial line, that is when the density of $S$ is $\Delta_{k,n}= |S|/k^n$ where $k\geq 3$, $n\geq 1$. This result given as theorem \eqref{hka1} is complementary to  Oleg Verbitsky theorem \eqref{ver96}.

 \begin{thm} Let $k\geq 3$, $n\geq 1$ and $S\subseteq [k]^n$ with density $\Delta_{k,n}$. We have: 	
 $\val (G_S^n) \geq \Delta_{k,n}.$  \label{hka1}
 	\end{thm} 
For this  game $G_S$, according to the theorems \eqref{ver96} and \eqref{hka1}, we conclude that $\val (G_S^n)=\Delta_{k,n}.$

To prove  the theorem \eqref{hka}, we need to construct a game which  satisfies the conditions on theorem \eqref{hka}. So, let us construct a game $G_S$   as  defined by \cite{hkazla2016forbidden} based to the subset $S $ of the set $[k]^n$. 

Let $k \geq 3$, $n \geq 1$ and $S \subseteq [k]^n$ with $\delta (S)= \frac{|S|}{k^n}$. The game $G_S$ with question set $Q_k$ which we will define must satisfy the  following requirements: 
\begin{itemize}
\item If $S$ does not contain a combinatorial line, then $G_S$ is non-trivial. \item $\val (G_S^n) \geq \delta (S).$
\end{itemize}

As $|Q_k|=k$ and $|[k]|=k$, there is a natural bijection between the question tuples in $Q_k$ and $[k]$. So, the game $G_S$ is played as this. The verifier chooses the number of a special prover $t \in [k]$   and sends $1$ to the special prover and $0$ to all other provers. 
The answer set of the game $G_S$ is the same for all provers: $A^t=2^{[n]} \times [n]$ where the power set  $2^{[n]}$ denotes the set of all subsets of $[n]$. Note that the set $2^{[n]}$ is equivalent to the set $\{1,2,\ldots, 2^n\}.$ Thus, answers from provers are in the form $(T^1, z^1), \ldots, (T^k, z^k)$. The verifier checks the following conditions and accepts if all of them are met: 
\begin{itemize}
\item The sets $T^1, T^2,\ldots, T^k$ form a partition of $[n].$
\item $z^1=z^2=\ldots=z^k=z.$
\item $z \in T^t$
\item Let $\bar{s} = (s_1, s_2, \ldots, s_n)$ be the string over $[k]^n$ such that  $s_i = e$ if and only if $i \in  T ^e$ for $1\leq i \leq n.$ Then, $\bar{s} \in S.$
\end{itemize}

From the definition of the game $G_S$ we can deduce the following propositions given and proved by \cite{hkazla2016forbidden}. So, the proofs of these propositions are adapted from this latter paper.  
\begin{pro} If $S$ has a combinatorial line, then the game $G_S$ is trivial	. \label{pr1}	\end{pro}
%\Jnote{You have to define $G_S$ before stating the proposition.}
\begin{proof}
We assume that $S \subseteq [k]^n$ has a combinatorial line. 
Let $\bar{b}=w(x)=(b_1,\ldots, b_n)$ an $x-$string for which the  combinatorial line is $L(\bar{b})=\{w(x;i): i \in [k]\} \subseteq S$ and let fix a position $z \in [n]$ with $b_z=x$. Note that $b_1,\ldots, b_n \in [k] \cup \{x\}$. For $p \in [k] \cup \{x\}$, let us define a set $B(p)$ as: $B(p)=\{j: b_j=p\}$. The set $B(p)$ is the set of coordinates $j$ in which $b_j$ equals  to $p.$ Now, let us define the  strategy for which prover $e$ will use to answer questions:
$$ f^e(q^e)=\left\lbrace \begin{array}{ll} (B(e),z) & \text{if } q^e=0, \\ (B(e) \cup B(x), z) & \text{if } q^e=1.\end{array} \right. $$

Thus, the verifier checks the four conditions. The verifier will always accept the first condition because the sets $B(1), \ldots, B(k), B(x)$ from a partition. All $z^e$ are equal, that is $z^1=\ldots=z^k$, then the second condition is satisfied. Because the prover $t$ responds with  $(B(t) \cup B(x), z)$ and $z \in B(x)$, then $z \in T^t$: the third condition is satisfied. The fourth condition is also satisfied because $\bar{s}=\bar{b}$ with $t$ in place of stars and $\bar{s}=\bar{b} =w(t) \in L(\bar{b}) \subseteq S.$
\end{proof}

\begin{pro} If the game $G_S$ is trivial, then $S$ has a combinatorial line.	 \label{pr2}	\end{pro}

\begin{proof}
We assume that the game $G_S$ is trivial. So, let $f^1, \ldots, f^k$ be a strategy for the provers that always wins. The form of the answer of the prover $e$ to the question $q \in \{0,1\}$ is defined as: $(T_q^e, z_q^e)=f^e(q)$ where $e \in [k]$.  Since whenever $e \neq t$, the verifier checks $z_0^e=z_1^a$. As the game is trivial we have $z_0^1=z_0^2= \ldots=z_0^k=z_1^1=z_1^2= \ldots=z_1^k=z$. 
For any two $e\neq e'$, $T_0^e \cap T_0^{e'}= \emptyset$, that the two sets $T_0^e $ and $T_0^{e'}$ are pairwise disjoint. If $t \neq e$ and $a\neq e'$, the verifier will reject.
$z \in T_0^1 \cup \ldots \cup T_0^k$, since if $z \in T_0^e$, the verifier rejects if $t \neq e$. Therefore, the word $\bar{b}=w(x)$ (combinatorial line)  is defined as: $$b_i=\left\lbrace \begin{array}{ll} e & \text{if } i \in T_0^e, \ \text{for }j \in [k], \\ x & \text{ otherwise}.\end{array} \right.$$
For a fix $t \in [k]$, $w(t) \in S.$ We suppose that  the verifier picks $t$ as the special prover. Since the verifier checks that the sets $T^e$ form a partition, it must be that prover $t$ responds with $T_1^t=[n] \ \left(T_0^1 \cup \ldots \cup T_0^{t-1} \cup T_0^{t+1} \cup \ldots T_0^k	 \right) .$ The verifier checks that the resulting string is in $S$ and accepts, it must be that $w(t) \in S.$ This holds for every $t$, and thus $L(\bar{b}) \subseteq S.$
\end{proof}

\begin{pro}	 The value of $G_S^n$ is at least $\delta(S)$	  \label{pr3} \end{pro}

\begin{proof}
Let  $T^e=\{i \in [n]: q_i^e=1\}$. $T^e$ defines the set of coordinates in which prover $e$ is special. In coordinate $i$, prover $e$ responds with $(T^e,i).$ Let $a_1, \ldots, a_n$ be the sequence of special provers which the verifier picks. Let us assume that if $(a_1, \ldots, a_n) \in S$ then the verifier accepts in all coordinates with probability $\delta(S).$ 

Let us show that $\bar{s}=(a_1, \ldots, a_n) $. Since in each coordinate there is exactly one special prover, then the sets $T^1, \ldots, T^k$ form a partition of $[n]$. $z_i^1=\ldots=z_i^k=i \in T^{t_i}$ by definition of $T^e$ and since prover $t_i$ is pecial in coordinate $i.$ Therefore, $\bar{s} \in S$, since for all $n$ coordinates $\bar{s}$ is exactly the string $(a_1, \ldots, a_n).$
\end{proof}

\Jnote{The language you use in these three propositions cannot be so close to
  what we have in our paper. You should write these proofs
  \emph{in your own words}. This means while writing you 
  \emph{should not be looking at my paper}.}



%A short proof of the theorem \eqref{hka} has been given by \cite{hkazla2016forbidden} by using the proposition \eqref{prop} and theorem \eqref{hhm} which contain  the notion of \textit{homomorphism} of question sets. Let us introduce notions of homomorphism.
%
%Let $k\geq 2$ and $Q \subseteq X^1 \times \ldots \times X^k$ be a $k-$prover question set. Consider the $r-$regular, $r-$partite hypergraph\footnote{A hypergraph is pair $(X,E)$ where $X$ is a set of elements called \textit{nodes} or \textit{vertices}, and $E$ is a set of non-empty subsets of $X$ called hyperedges (set of nodes) or edges. For further reading, see https://en.wikipedia.org/wiki/Hypergraph} $G=(X^1 \times \ldots \times X^k, Q).$
%
% Given two hypergraphs $(X^1 \times \ldots \times X^k, Q)$ and $(Y^1 \times \ldots \times Y^k, P)$. The function $f=(f^1, \ldots, f^k)$ where $f^t: X^t \longrightarrow Y^t$ is a homomorphism from $Q$ to $P$ if $\bar{q}=(q^1, \ldots,q^k) \in Q$ implies $f(\bar{q})=(f^1(q^1), \ldots,f^k(q^k)) \in P.$
%
%Let $S\subseteq Q^n$ with $\delta(S)= |S|/|Q^n|$ the density of $S$, and $f=(f_1, \ldots, f_n)$ be a vector of $n$ homomorphisms of $Q$ (from $Q$ to $Q$). $f$ is \textit{good} for $S$ if:
%\begin{itemize}
%\item For every $\bar{q}=(q^1, \ldots,q^k) \in Q$, we have $f(\bar{q})=(f_1(\bar{q}), \ldots, f_n(\bar{q})) \in S.$
%\item There exists $i \in  [n]$ such that $f_i$ is identity.
%\end{itemize}
%
%\Jnote{Please summarize the direct proof, not the one with homomorphisms.}
%
%\begin{thm}[\cite{feige1996error}]	Let $Q$ be a connected, $k-$prover question set and $S \subseteq Q^n$. There exists an $k-$prover game $G_S$ with question set $Q$ such that:
%\begin{itemize}
%\item If $G^S$ is trivial, then there exists a homomorphism vector $f$ that is good for $S$.
%\item $\val (G_S^n) \geq \delta.$
%\end{itemize} \label{hhm}	\end{thm} 
%
%\begin{pro}	Let $r \geq 3$ and $S \subseteq Q_k^n \cong [r]^n$ such that there exists a homomorphism vector $f$ that is good for $S$. Then, $S$ contains a combinatorial line.	\label{prop}\end{pro}
% 
%Moreover, let us consider that $S$ is a subset of $[k]^n$ without a combinatorial line. Assume that $S$ is the maximum subset of $[k]^n$ without a combinatorial line, then from theorem \eqref{hka} we obtain the theorem \eqref{hkb} which is a  complementary inequality to theorem \eqref{ver96}.
% 
% \begin{thm}[\cite{hkazla2016forbidden}] For $k \geq 3$, $\Delta_{k,n}	\leq \val (G^n).$ \label{hkb}	\end{thm}
% 
% Considering that $\nu_{Q,n}=\max_G \val (G^n)$ where the maximum is over all non-trivial games $G$ with question set $Q$, we have $\Delta_{k,n}	\leq \nu_{Q,n}$ which remains true.
% 
% By combining the two theorems \eqref{ver96} and \eqref{hkb}, we have $\val (G^n)=\Delta_{k,n}.$. Likewise, the maximum  value of  all non-trivial games equals to the density of the maximum subset of $[k]^n$ without a combinatorial line, that is $\nu_{Q,n}=\Delta_{k,n}.$
% 
%From the best known lower bound of $\Delta_{k,n}$ established by \cite{polymath2010density}, we can apply it to bound $\val (G^n)$. This lower bound adapted by \cite{hkazla2016forbidden}, thereafter for this kind of multi-prover is formulated in \eqref{hkc}
% 
% \begin{thm}Let $\ell \geq 1$ and $k=2^{\ell-1}+1.$ There exists $C_{\ell} >0$ such that for every $n\geq 2$ there exists a set $S \subseteq [k]^n$ with $$ \delta(S) \geq \exp \left( -C_{\ell} (\log n)^{1/\ell} \right)$$	 such that $S$ does not contain a combinatorial line  \label{hkc}	\end{thm}
%
% As $\val (G_S^n) \geq  \delta(S)$, we deduce from \eqref{hkc} that  $\val (G_S^n) \geq  \exp \left( -C_{\ell} (\log n)^{1/\ell} \right)$ for $k=2^{\ell-1}+1.$
%
% \Jnote{The section with proofs seems disorganized. Please divide it clearly
%   into two parts (DHJ => PR) and (PR => DHJ) without mixing them up.}
% 